\section{Conclusions}
The Hill sphere transits of \pic c lead to the search for the 1981 event. ASTEP, bRing and BRITE covered \pic c during two primary transits at MJD $\text{58210} \substack{+\text{28} \\ -\text{42}}$ and $\text{59413} \substack{+\text{10} \\ -\text{11}}$ and a secondary transit at $\text{58707}\substack{+\text{5} \\ -\text{8}}$. All transits and additional discontinuous coverage spanning from 03-02-2017 to 17-01-2023 were fitted to a model of the 1981 event to search for compelling evidence of a similar detection, however none was found. Unknown pulsations with a magnitude increase to $a \sim$ 0.01 over a span 5-15 day by ASTEP and bRing were discovered, possibly due to ground-based sources. 

Moreover, the circumplanetary disk's tilt and inclination was probed at 0.3 and 0.6$r_{\text{Hill}}$ using a model from \cite{Kenworthy_2021}. The model's sensitivity to the midpoint of the offset was analysed, showing partial tracebacks to the correct orientation up to three days. Thereafter, no signs of a disk were detected. Taking the sensitivity of the model into account, the optical depth at the primary transits MJD 58210 and MJD 59413 at 0.3 and 0.6$r_{\text{Hill}}$ were computed. The former transit has a coverage from all instruments and a disk bias towards inclinations smaller than 30\textdegree \ and inclinations larger than 60\textdegree. bRing has the highest SNR, however negative optical depths, while ASTEP and BRITE have low SNR and positive optical depth. The latter transit was only covered by bRing with a bias towards larger inclinations and positive optical depth values. Thus, the results are inconsistent for the different instruments at MJD 58219 and inconsistent among both transits. The poorly constrained midpoints of the transits and the highly sensitive model yield inconclusive results. Therefore more coverage, tighter orbital constraints and a modified CPD disk model are required for future research. One of the exciting missions of the near future called PLATO, could reward us with the open-ended questions of this paper.